Inputing Weights

### 2023-05-18 src/03_input_weights.Rmd
updating data folder structures

```{r echo=FALSE}
# list of MSAs without filtering population size
unfiltered_msas <- read_csv(here("data/intermediate/unfilter_msas.csv"))
real_estate_metrics <- read_csv(here("data/intermediate/demographic_data.csv")) %>% 
  select(cbsa, anchor_city, msa, starts_with("n_")) %>% 
  mutate(cbsa = factor(cbsa))

>>>>

```{r echo=FALSE}
# list of MSAs without filtering population size
unfiltered_msas <- read_csv(here("data/intermediate/unfilter_msas.csv"))

real_estate_metrics <- read_csv(here("data/intermediate/n_real_estate_metrics.csv")) %>% 
  select(cbsa, anchor_city, msa, starts_with("n_")) %>% 
  mutate(cbsa = factor(cbsa))
